Data Analysis and Modeling

### 2018-07-19 review/response_to_reviewers.Rmd

 * We do agree that on-going (month by month) maintenance costs will likely be higher in an STR, however, large improvements, new carpets, painting, etc. do burden LTRs at tenant turnover.  As we mentioned on page 6, we believe there is an argument to be made that LTR tenants actually burden a property as much if not more by virtue of moving furniture in and out, hanging decorations and, likely, spending more actual time in the dwelling than a tourist would.  As a result of this and the fact that we were not able to find any evidence of greater maintenance costs on either side, we decided on assumming equivalent costs.

  * Certainly there are time costs of managing an STR.  These costs vary widely based on the owner's proximity to the STR and their individual imputed wage (the value of their time).  In general, these costs are somewhat idiosyncratic to the owner and we struggled with producing a standardized estimate.  On the converse, STR does allow for an early exit strategy, occupation or transfer to LTR on short notice, options which also have an unknown (or at least very owner-specific) value.  We opted to allow these two forces to 'balance' out and have not accounted for either.  The intent of the hypothetical exercise was to present the case of a simple investor (say a family) making one investment, not a large STR aggregation firm.  Note that there are firms in Melbourne and other cities that will manage your Airbnb for you.  Anecdotally, we've seen fees ranging from 8% to 15% for this service.

  * All of the above concerns seem to point to a potential underestimate of STR costs, which would lower STR net revenues.  As a further senitivity analysis, we reduced net STR revenues by 15% (10% for management fee and 5% for a furnishing costs), the results of which are found in the Table below. These should be compared to Table 2 in the paper.  Reducing STR revenues by 15% has the likely impact of decreasing the base rate of STR preference from 28% down to 22% (also evidenced in the intercept terms Table 1.)  The coefficients on the set of variables tested (while moving) have generally remained stable in both terms of magnitude and direction.  We feel that your comments regarding management and furniture are worthwhile.  We worry about adding another table of sensitivity results to the paper in terms of confusion.  We have added additional language to the Discussion section to note these omission, explain our rationale for doing so and discuss the sensitivity test shown in Table 1 of this response.

```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}

  library(tidyverse)
  library(sf)
  library(geosphere)
  library(ggmap)
  library(multidplyr)
  library(tmap)
  library(xtable)
  library(ROCR)
  library(xtable)

```

```{r options_functions, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}

  options(stringsAsFactors=FALSE)
  options(xtable.comment = FALSE)
  options(xtable.caption.placement='top')
  setwd('..')
  source(file.path(getwd(), 'functions', 'abb_Functions.R'))

```

```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, results='hide'}

  setwd('..')
  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data_15s.RData'))

```

```{r log_model, echo=FALSE, message=FALSE, comment=FALSE}

 ## Extract data

  m1 <- as.data.frame(summary(lik_glms$str)$coefficients)
  m2 <- as.data.frame(summary(lik_glms$loc)$coefficients)
  m3 <- as.data.frame(summary(lik_glms$host)$coefficients)

 ## Create vector with significance stars

  m1sig <- makeStatSig(m1[ ,4])
  m2sig <- makeStatSig(m2[ ,4])
  m3sig <- makeStatSig(m3[ ,4])

 ## Create coefficients for the table (with stars)

  m1$table.coef <- paste0(ifelse(m1$Estimate>0, ' ', ''),
                          sprintf('%.3f', round(m1$Estimate,3)),
                          m1sig)
  m2$table.coef <- paste0(ifelse(m2$Estimate>0, ' ', ''),
                          sprintf('%.3f',round(m2$Estimate,3)),
                          m2sig)
  m3$table.coef <- paste0(ifelse(m3$Estimate>0, ' ', ''),
                          sprintf('%.3f',round(m3$Estimate,3)),
                          m3sig)

 ## Even out the lengths

  m1c <- c(m1$table.coef, rep(' ', nrow(m3)-nrow(m1)))
  m2c <- c(m2$table.coef, rep(' ', nrow(m3)-nrow(m2)))
  m3c <- m3$table.coef

 ##  Create the variable section of table
 full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
 names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
                          'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)',
                          'Beach (Submarket)', 'Guests per Bedroom',
                          'Minimum Stay', 'Flexible Cancel')

 ## Create model diagnostics

  # Extract diagnostics
  str.dx <- logDx(lik_glms$str, str_tdf, str_tdf$lik_pref)
  sm.dx <- logDx(lik_glms$loc, str_tdf, str_tdf$lik_pref)
  host.dx <- logDx(lik_glms$host, str_tdf, str_tdf$lik_pref)

  # Create diagnostic table
  diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
                                      'AUC'),
                           Str.Model=c('', '', round(str.dx$AIC,0),
                                       round(str.dx$logLik, 0),
                                       round(as.numeric(str.dx$auc@y.values),
                                             3)),
                           Sm.Model=c('', '', round(sm.dx$AIC,0),
                                      round(sm.dx$logLik, 0),
                                      round(as.numeric(sm.dx$auc@y.values), 3)),
                           Host.Model=c('', '', round(host.dx$AIC,0),
                                        round(host.dx$logLik, 0),
                                        round(as.numeric(host.dx$auc@y.values),
                                              3)))
  names(diag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")

 ## Combine into full table

  full.table <- rbind(full.table, diag.table)
```

```{r table_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}

  # XTable
  x.full <- xtable(full.table,
                  caption='Logistic Modeling Results (15% Cost Increase: Likely Revenue)\n')
  align(x.full) <- 'lllll'

  # comment          <- list()
  # comment$pos      <- list()
  # comment$pos[[1]] <- c(nrow(x.full))
  # comment$command  <- c("your footnote, caption or whatever.  \n")

  # Print
  print(x.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,16,21,21),
       # add.to.row = comment,
       caption.placement='top')

```

@@

* Great point.  The short-term market for large, natural amenitiy-rich (ski + beach) properties is decades (if not centuries old).  We believe that Airbnb and its sister-sites have opened up this market to small, urban properties as well decreased search costs to the point that, from an owner perspective,  very short stays, even of a single night, can be economically feasible.  We have updated the abstract to represent the distinction that you have made.

b) *The next sentence in the abstract states “In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.” I think sitations is a typo. I only point it out because it is in the abstract.*

* Thank you for pointing out this typographic error.  We have corrected it.

6. *The tables and figures do not have any supporting notes.*

 * We are unclear as to what sort of supporting notes are desired.   Information on data sources are provided in the accompanying text.  We are happy to add whatever is necessary to help the reader, if you can provide some examples here.

### 2018-07-19 papers/full_paper.Rmd
Review: Response to reviewer 2

---
title: "To Airbnb?: A Question of Revenue"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "May 30th, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

@@

  options(stringsAsFactors=FALSE)
  options(xtable.comment = FALSE)
  options(xtable.caption.placement='top')
  setwd('..')
  source(file.path(getwd(), 'functions', 'abb_Functions.R'))

@@

  setwd('..')
  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

@@

In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.  We have done so as we were unable to location any evidence to suggest that one was higher than the other.  This may be a limitation of our study and could prove to be an avenue of future research.

>>>>

---
title: "To Airbnb?: A Question of Revenue"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "July 22nd, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

@@

  options(stringsAsFactors=FALSE)
  options(xtable.comment = FALSE)
  options(xtable.caption.placement='top')
  setwd('..')
  #source(file.path(getwd(), 'functions', 'abb_Functions.R'))
  source(file.path('c:/code', 'research', 'airbnbMelbourne', 'functions', 'abb_Functions.R'))

@@

  # setwd('..')
  # load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
  load(file.path('c:', 'code', 'research', 'airbnbMelbourne','data', 'analyzed',
                 'analyzed_data.RData'))

@@

In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.  We have done so as we were unable to location any evidence to suggest that one was higher than the other. Additionally, in the reported results we have not made allowances for furniture and the turnover costs associated with managing an STR.  This omission is intentional as we felt these costs were highly idiosyncratic (turnover) and/or not limited to the one-year scenario period (furniture).  Sensitivity tests on these two costs (both of which lower STR revenues) do create decrease in the base rate of STR preference, but show little change to the coefficients across the various regression models. There is limited research around STR rental hosting costs and this uncertainty around cost estimates is a limitation of our study and could prove to be an avenue of future research.

### 2018-07-19 scripts/4_data_analysis_15s.Rmd
Review: Response to reviewer 2

  dir.create(file.path(getwd(), 'data', 'analyzed'))
  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

>>>>

  dir.create(file.path(getwd(), 'data', 'analyzed'))
  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data_15s.RData'))
